Componentes Passivos em RF

### 2024-11-27 Lab09 - IP3-meas_prj/Docs/article/article.qmd
asdkhjfaklsdjhflkasdf

```{=latex}
\begin{figure}[h]
  \centering
  \begin{circuitikz}[american]
    \draw (1.98, -0.5) node[npn](nmos1){};
    \draw (nmos1.C) to[short] ++(0, 0.23) to[short, i^<=$I_C$] ++(3.52, 0) to[battery1, l=$V_{cc}$] ++(0, -4) node[ground]{} ;
    \draw (nmos1.E) to[isource, l=$I_{ee}$] (2, -3.5) node[ground]{} ;
    \draw (-0.5, -3.5) node[ground]{} to[sV, l=$V_{s2}$] ++(0, 1.5) to[sV, l=$V_{s1}$] ++(0, 1.5) to[battery1, l=$V_B$, invert] (nmos1.B) ;
    \draw (2, -1.5) to[short] ++(2, 0) to[C, l=$C$] ++(0, -2) node[ground]{} ;
  \end{circuitikz}
  \caption{Circuito com o BJT}
  \label{fig:circuit-bjt-original}
\end{figure}
```

@@

```{=latex}
\begin{figure}[h]
  \centering
  \begin{circuitikz}[american]
    \draw (1.98, -0.5) node[npn](nmos1){};
    \draw (nmos1.C) to[short] ++(0, 0.23) to[short, i^<=$I_C$] ++(3.52, 0) to[battery1, l=$V_{cc}$] ++(0, -5) node[ground]{} ;
    \draw (-0.5, -4.5) node[ground]{} to[sV, l=$V_{s2}$] ++(0, 1.5) to[sV, l=$V_{s1}$] ++(0, 2.5) to[battery1, l=$V_B$, invert] (nmos1.B) ;
    \draw (2, -3) coordinate(point1) to[isource, l=$I_{ee}$] ++(0, -1.5) node[ground]{} ;
    \draw (point1) to[short] ++(2, 0) to[C, l=$C$] ++(0, -1.5) node[ground]{} ;
    \draw (point1) to[R, l=$R_E$] (nmos1.E) ;
  \end{circuitikz}
  \caption{Circuito com $R_E$}
  \label{fig:circuit-bjt-RE}
\end{figure}
```

>>>>

```{=latex}
\begin{figure}[h]
  \centering
  \begin{circuitikz}[american]
    \draw (1.98, -0.5) node[npn](nmos1){};
    \draw (nmos1.C) to[short] ++(0, 0.23) to[short, i^<=$I_C$] ++(3.52, 0) to[battery1, l=$V_{cc}$] ++(0, -4) node[ground]{} ;
    \draw (nmos1.E) to[isource, l=$I_{ee}$] (2, -3.5) node[ground]{} ;
    \draw (nmos1.B) to[short] ++(-1.65, 0) coordinate(point1) ;
    \draw (-0.5, -3.5) node[ground]{} to[sV, l=$V_{s2}$] ++(0, 1.5) to[sV, l=$V_{s1}$] (point1) ;
    \draw (1.99, -1.5) to[short] ++(2, 0) to[C, l=$C$] ++(0, -2) node[ground]{} ;
  \end{circuitikz}
  \caption{Circuito com o BJT}
  \label{fig:circuit-bjt-original}
\end{figure}
```

@@

```{=latex}
\begin{figure}[h]
  \centering
  \begin{circuitikz}[american]
    \draw (1.98, -0.5) node[npn](nmos1){};
    \draw (nmos1.C) to[short] ++(0, 0.23) to[short, i^<=$I_C$] ++(3.52, 0) to[battery1, l=$V_{cc}$] ++(0, -5) node[ground]{} ;
    \draw (-0.5, -4.5) node[ground]{} to[sV, l=$V_{s2}$] ++(0, 1.5) to[sV, l=$V_{s1}$] ++(0, 2.5) to[short] (nmos1.B) ;
    \draw (2, -3) coordinate(point1) to[isource, l=$I_{ee}$] ++(0, -1.5) node[ground]{} ;
    \draw (point1) to[short] ++(2, 0) to[C, l=$C$] ++(0, -1.5) node[ground]{} ;
    \draw (point1) to[R, l=$R_E$] (nmos1.E) ;
  \end{circuitikz}
  \caption{Circuito com $R_E$}
  \label{fig:circuit-bjt-RE}
\end{figure}
```
